---
title: "Flu-Edinburgh colaboration"
author: "Oscar de León"
date: "May 20, 2017"
output: pdf_document
---

```{r setup, include=FALSE}
# Load used packages
library(package = "lubridate")
library(package = "tidyverse")


# Define study metadata
study_years <- 2010:2016
study_sites <- c("H-Cuilapa", "H-Xela")


# Setup knitting
knitr::opts_knit$set(root.dir = "..")
knitr::opts_chunk$set(echo = FALSE, message = FALSE, warning = FALSE)
```



```{r load-data}
# Run data preparation scripts
source(file = "scripts/get-server-data.R")
source(file = "scripts/get-population-data.R")
```



```{r clean-data}
# Catchment
catchment <- catchment %>%
  # Fix casing
  mutate_at(
    vars(department, municipality),
    funs(
      gsub(
        "(^| )([a-z])", "\\1\\U\\2",
        tolower(iconv(., to = "ASCII//TRANSLIT")),
        perl = TRUE
      )
    )
  ) %>%
  # Fix typos
  mutate(
    municipality = recode(
      municipality,
      "Santa Cruz Naranajo" = "Santa Cruz Naranjo",
      "Concepcion Chiquirichap" = "Concepcion Chiquirichapa",
      "San Martin Sacatepeque" = "San Martin Sacatepequez"
    )
  )


# Surveillance data
all_respi <- all_respi %>%
  # Fix casing
  mutate_at(
    vars(case_department, case_municipality),
    funs(
      gsub(
        "(^| )([a-z])", "\\1\\U\\2",
        tolower(iconv(., to = "ASCII//TRANSLIT")),
        perl = TRUE
      )
    )
  ) %>%
  # Label variables
  mutate(
    # Site department
    site_department = recode(
      site_department,
      "QU" = "Quetzaltenango",
      "SR" = "Santa Rosa"
    ),
    # Location for population
    site_location = recode(
      site_name,
      "H-Cuilapa" = "Santa Rosa",
      "H-Xela" = "Quetzaltenango",
      "CS-NSR" = "Nueva Santa Rosa"
    ),
    # Label age groups
    age_group = case_when(
      age_years == 0 & age_months == 0 & age_days < 28 ~ "0-27 days",
      age_years == 0 & age_months < 3 ~ "28 days-<3 month",
      age_years == 0 & age_months < 6 ~ "3-5 months",
      age_years == 0 & age_months < 9 ~ "6-8 months",
      age_years == 0 & age_months < 12 ~ "9-11 months",
      (age_years == 0 & age_months == 12) |
        between(age_years, 1, 1) ~ "12-23 months",
      between(age_years, 2, 2) ~ "24-35 months",
      between(age_years, 3, 4) ~ "36-59 months",
      TRUE ~ NA_character_
    ),
    age_group = factor(age_group, levels = labels_age_groups, ordered = TRUE)
  ) %>%
  # Only keep cases under 5 yoa
  filter(
    !is.na(age_group),             # Defined age groups
    year %in% study_years          # During the study period
  )


# Population data
catchment_population <- population %>%
  # Tag as catchment area
  left_join(catchment) %>%
  filter(catchment == 1) %>%
  # Tag locations for hospitals
  mutate(location = department) %>%
  # Tag locations for NSR
  bind_rows(
    mutate(
      filter(., municipality == "Nueva Santa Rosa"),
      location = municipality
    )
  ) %>%
  # Summarize population for each location, year and age group
  group_by(location, age_group, year) %>%
  summarize(population = sum(population)) %>%
  ungroup()
